Full-depth Coadds of the WISE and First-year NEOWISE-Reactivation Images

### 2016-03-01 ms.tex
added DECaLS reference, clean-up of DECaLS DR1 versus DR2 explanation

The only existing catalogs based on our AllWISE+NEOWISER W1/W2 coadds
are forced photometry catalogs corresponding to DECam Legacy
Survey\footnote{http://legacysurvey.org} (DECaLS) DR2 optical sources. 
Optical sources from DECaLS DR1 are accompanied by forced based on the
\cite{lang14} W1/W2 coadds. Therefore, comparing the S/N of W1/W2
fluxes in DR2 versus DR1 allows us to obtain a preliminary estimate of the 
increased depths in regions of low ecliptic and high galactic latitude.

>>>>

The only existing catalogs based on our AllWISE+NEOWISER coadds
are those from DR2 of the DECam Legacy Survey\footnote{http://legacysurvey.org} 
\citep[DECaLS;][]{decals}, which include W1-W4 forced photometry for all
optically detected sources. On the other hand, optical sources in DECaLS DR1
are accompanied by forced photometry of the \cite{lang14} unWISE coadds. 
Therefore, comparing the S/N of W1/W2 fluxes in DR2 versus DR1 can allow us to 
obtain estimates of the depth increases for regions of low ecliptic and high 
galactic latitude.
